---
title: "RAboot"
author: "Yuto Kitano"
date: "2024-08-13"
output:
  pdf_document: default
header-includes:
- \usepackage{booktabs}
- \usepackage{caption}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(tidyverse)
```

# Formatting Data

## Formatting Semester Data

```{r}
setwd("/Users/kitanoyuuto/Downloads/warmup training package/01_data/raw/semester_dummy")
semester_1 <- read.csv("semester_data_1.csv", header = TRUE, skip = 1)

semester_2 <- read.csv("semester_data_2.csv")  

colnames(semester_2) <- colnames(semester_1)

semester_data <- rbind(semester_1, semester_2) %>% 
  select(-Y)

semester_data <- semester_data %>%
  group_by(unitid) %>%
  mutate(semester_start_year = ifelse(any(semester == 1), min(year[semester == 1]), NA))

semester_data <- semester_data %>% 
  mutate(semester_flag = ifelse(year >= semester_start_year, 1, 0))

```

## Formatting Gradrate Data

```{r}
library(readxl)
library(purrr)
library(stringr)

file_paths <- list.files(path = "/Users/kitanoyuuto/Downloads/warmup training package/01_data/raw/outcome", pattern = "*.xlsx", full.names = TRUE)
valid_file_paths <- file_paths[!str_detect(file_paths, "~\\$")]

data_list <- map(valid_file_paths, read_excel)


graduate_data <- bind_rows(data_list) %>% 
  filter(year <= 2010) %>% 
  mutate(
    tot4yrgrads = as.numeric(tot4yrgrads),
    totcohortsize = as.numeric(totcohortsize),
    women_gradrate_4yr = as.numeric(women_gradrate_4yr),
    m_4yrgrads = as.numeric(m_4yrgrads),
    m_cohortsize = as.numeric(m_cohortsize)
  ) %>% 
  mutate(
    w_grad = round(women_gradrate_4yr * 0.01,3),
    t_grad = round(tot4yrgrads / totcohortsize,3),
    m_grad = round(m_4yrgrads / m_cohortsize,3)
  )

```

## Formatting Covariates Data

```{r}
setwd("/Users/kitanoyuuto/Downloads/warmup training package/01_data/raw/covariates")

covariates <- read_xlsx("covariates.xlsx") %>% 
  rename("unitid" = "university_id")

covariates <- covariates %>%
  mutate(unitid = str_replace_all(unitid, "aaaa", ""))

cov_wide <- covariates %>%
  pivot_wider(names_from = category, values_from = value, 
              values_fill = NA,
              id_cols = c(unitid, year)) %>% 
  filter(year >= 1991 & year <= 2010)

id <- unique(semester_data$unitid)

cov_wide <- cov_wide %>% 
  filter(cov_wide$unitid  %in% id) %>% 
  mutate(year = as.numeric(year)) %>% 
   mutate(unitid = as.numeric(unitid))
  
```

## Left_Join

```{r}
data <- left_join(semester_data, graduate_data , by = c("unitid", "year"))

data <- left_join(data, cov_wide, by = c("unitid", "year"))

```

# Descriptive Statistics

## Table

```{r}

data_nt <- data %>% 
  group_by(unitid) %>% 
  mutate(mean_quarter = mean(quarter, na.rm = TRUE)) %>%  
  filter(mean_quarter == 1) %>%
  ungroup()

data_at <- data %>% 
  group_by(unitid) %>% 
  mutate(mean_quarter = mean(quarter, na.rm = TRUE)) %>%  
  filter(mean_quarter != 1) %>%
  ungroup()


summarise <- data %>% 
  ungroup() %>%  
  summarise(
    totcohortsize = mean(totcohortsize, na.rm = TRUE),
    w_cohortsize = mean(w_cohortsize, na.rm = TRUE),
    m_cohortsize = mean(m_cohortsize, na.rm = TRUE),
    t_grad = mean(t_grad, na.rm = TRUE),
    w_grad = mean(w_grad, na.rm = TRUE),
    m_grad = mean(m_grad, na.rm = TRUE)
  )

summarise_nt <- data_nt %>% 
  ungroup() %>%  
  summarise(
    totcohortsize = mean(totcohortsize, na.rm = TRUE),
    w_cohortsize = mean(w_cohortsize, na.rm = TRUE),
    m_cohortsize = mean(m_cohortsize, na.rm = TRUE),
    t_grad = mean(t_grad, na.rm = TRUE),
    w_grad = mean(w_grad, na.rm = TRUE),
    m_grad = mean(m_grad, na.rm = TRUE)
  )

summarise_at <- data_at %>% 
  ungroup() %>%  
  summarise(
    totcohortsize = mean(totcohortsize, na.rm = TRUE),
    w_cohortsize = mean(w_cohortsize, na.rm = TRUE),
    m_cohortsize = mean(m_cohortsize, na.rm = TRUE),
    t_grad = mean(t_grad, na.rm = TRUE),
    w_grad = mean(w_grad, na.rm = TRUE),
    m_grad = mean(m_grad, na.rm = TRUE)
  )

summarise_all <- summarise %>%
  pivot_longer(cols = everything(), names_to = "Variable", values_to = "All_Data")

summarise_nt_long <- summarise_nt %>%
  pivot_longer(cols = everything(), names_to = "Variable", values_to = "Control_Group")

summarise_at_long <- summarise_at %>%
  pivot_longer(cols = everything(), names_to = "Variable", values_to = "Treatment_Group")

summarise_at_long$Variable

summary_table <- cbind(
  summarise_all$All_Data,
  summarise_nt_long$Control_Group,
  summarise_at_long$Treatment_Group
)

colnames(summary_table) <- c("All_Data", "Control_Group", "Treatment_Group")

rownames(summary_table) <- c("totcohortsize", "w_cohortsize", "m_cohortsize", "t_grad", "w_grad", "m_grad")

summary_table <- as.data.frame(summary_table)

library(xtable)



```

\begin{table}[ht]
\centering
\begin{tabular}{lccc}
  \toprule
 & All\_Data & Control\_Group & Treatment\_Group \\ 
  \midrule
totcohortsize & 1099.45 & 1695.19 & 1070.39 \\ 
  w\_cohortsize & 599.50 & 880.66 & 585.78 \\ 
  m\_cohortsize & 499.95 & 814.53 & 484.60 \\ 
  t\_grad & 0.37 & 0.38 & 0.37 \\ 
  w\_grad & 0.41 & 0.42 & 0.41 \\ 
  m\_grad & 0.32 & 0.33 & 0.32 \\ 
   \bottomrule
\end{tabular}
\caption{Summary Table} 
\end{table}

## Figure_grad

```{r}
data_fig <- data %>% 
  group_by(year) %>% 
  summarise(t_grad = mean(t_grad, na.rm = TRUE))

data_fig_2 <- data %>% 
  group_by(year) %>% 
  summarise(semester = mean(semester, na.rm = TRUE))

plot(x = data_fig$year, y = data_fig$t_grad, type = "l", xlab = "year", 
     ylab = "graduation rate")

plot(x = data_fig_2$year, y = data_fig_2$semester, type = "l", xlab = "year", 
     ylab = "ration of semester")

```

# Figure_semester

```{r}
plot(x = data_fig_2$year, y = data_fig_2$semester, type = "l", xlab = "year", 
     ylab = "ration of semester")


```

```{r}

plot(x = data_fig$year, y = data_fig$t_grad, type = "l", col = "blue",
     xlab = "Year", ylab = "Graduation Rate")

par(new = TRUE)

plot(x = data_fig_2$year, y = data_fig_2$semester, type = "l", col = "red",
     axes = FALSE, xlab = "", ylab = "")

axis(side = 4, at = pretty(range(data_fig_2$semester)))

mtext("Ration of Semester", side = 4, line = 3)

legend("topleft", legend = c("Graduation Rate", "Ration of Semester"),
       col = c("blue", "red"), lty = 1)


```




## Inference

```{r}
library(stargazer)
lm_model <- lm(t_grad ~ data$semester_flag, data = data)
```

\begin{table}[!htbp] \centering 
  \caption{} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{1}{c}{\textit{Dependent variable:}} \\ 
\cline{2-2} 
\\[-1.8ex] & t\_grad \\ 
\hline \\[-1.8ex] 
 semester\_flag & 0.122$^{***}$ \\ 
  & (0.013) \\ 
  & \\ 
 Constant & 0.251$^{***}$ \\ 
  & (0.013) \\ 
  & \\ 
\hline \\[-1.8ex] 
Observations & 13,243 \\ 
R$^{2}$ & 0.007 \\ 
Adjusted R$^{2}$ & 0.007 \\ 
Residual Std. Error & 0.224 (df = 13241) \\ 
F Statistic & 89.741$^{***}$ (df = 1; 13241) \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table} 
